Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-01 demystify.tex
updates

Also note that professors in a non-CS department unlikely can serve as formal PhD advisers for CS students (see \autoref{sec:related-fields}).

@@

However, if your goal is a PhD in CS, then you likely need to be in the CS dept \emph{and} advised by a CS faculty. A non-CS faculty may \emph{co-advise} or be in the PhD dissertation committee, but your main PhD adviser will likely be a tenured or tenure-track faculty in CS (\autoref{sec:faculty-types}). If in doubt, check with the CS department for their requirements.

>>>>

Also note that non-CS profs unlikely can serve as formal PhD advisers for CS students (see \autoref{sec:related-fields}).

@@

However, if your goal is a PhD in CS, then you likely need to be in the CS dept \emph{and} advised by a CS faculty. A non-CS faculty can serve in the PhD dissertation committee (common) or \emph{co-advise} (somewhat rare), but your main PhD adviser will likely be a tenured or tenure-track faculty in CS (\autoref{sec:faculty-types}). 
For example, a prof. in Stats or Math dept might be able to serve as a co-adviser, but not as a sole adviser of a student in a CS PhD program.  Similarly, a prof. in CS cannot serve as a formal adviser for a PhD student in a Math or Stats.
If in doubt, check with the CS department for their requirements.
